---
title: "Hip_Hop vs. Country"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Step 0. install and load needed libraries
```{r include = FALSE,warning = FALSE}
library(tm)
library(data.table)
library(tidytext)
library(tidyverse)
library(DT)
library(dplyr)
library(ggplot2)
library(wordcloud)
library(RColorBrewer)
library(SentimentAnalysis)
library(syuzhet)
library(SnowballC)
library(ggplot2)
library(RCurl)
library(topicmodels)
library(textmineR)
library(gplots)
```

### Step 1. Load the dataset lyrics.RData and generate needed subsets

Get 3 subsets from the file: 

1. new.RData - contains both genres, hiphop and country
2. hiphop.RData - contains genre hiphop only
3. country.RData - contains genre country only

```{r echo = FALSE}
load('/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/data/lyrics.RData') 

new <- dt_lyrics %>%
  filter(genre == 'Hip-Hop' | genre== "Country")

hiphop <-dt_lyrics %>%
  filter(genre == 'Hip-Hop')
# 8905
country <- dt_lyrics %>%
  filter(genre=="Country")
#7524
save(new, file="/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/output/new.RData")
save(hiphop, file="/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/output/hiphop.RData")
save(country, file="/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/output/country.RData")
```

### Step 2. Clean data

(Codes from the given Text_Processing.Rmd)

Clean the text by converting all the letters to the lower case, and removing punctuation, numbers, empty words and extra white space, and stem words then generate the corpuses.

```{r echo = FALSE}
# function for removimg leading and trailing whitespace from character strings 
leadingWhitespace <- content_transformer(function(x) str_trim(x, side = "both"))
# remove stop words
data("stop_words")
stop <- c(stop_words$word)
# clean the data and make a corpus
# Both--------------------------------------------------------------------------------------------------------------------
corpus_b <- VCorpus(VectorSource(new$lyrics))%>%
  tm_map(content_transformer(tolower))%>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(removePunctuation)%>%
  tm_map(removeWords, character(0))%>%
  tm_map(removeWords,stop)%>%
  tm_map(removeWords, c("lot", "today", "months", "month", "wanna", "wouldnt", "wasnt", "ha", "na", "ooh", "da",
        "gonna", "im", "dont", "aint", "wont", "yeah", "la", "oi", "nigga", "fuck",
          "hey", "year", "years", "last", "past", "feel","gotta","get","got","can")) %>%
  tm_map(removeNumbers)%>%
  tm_map(stripWhitespace)%>%
  tm_map(leadingWhitespace)%>%
  tm_map(stemDocument)

### hiphop---------------------------------------------------------------------------------------------------------------
corpus_h <- VCorpus(VectorSource(hiphop$lyrics))%>%
  tm_map(content_transformer(tolower))%>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(removePunctuation)%>%
  tm_map(removeWords, character(0))%>%
  tm_map(removeWords,stop)%>%
  tm_map(removeWords, c("lot", "today", "months", "month", "wanna", "wouldnt", "wasnt", "ha", "na", "ooh", "da",
        "gonna", "im", "dont", "aint", "wont", "yeah", "la", "oi", "nigga", "fuck",
          "hey", "year", "years", "last", "past", "feel","gotta","get","got","can")) %>%
  tm_map(removeNumbers)%>%
  tm_map(stripWhitespace)%>%
  tm_map(leadingWhitespace)%>%
  tm_map(stemDocument)

### country---------------------------------------------------------------------------------------------------------------
corpus_c <- VCorpus(VectorSource(country$lyrics))%>%
  tm_map(content_transformer(tolower))%>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(removePunctuation)%>%
  tm_map(removeWords, character(0))%>%
  tm_map(removeWords,stop)%>%
  tm_map(removeWords, c("lot", "today", "months", "month", "wanna", "wouldnt", "wasnt", "ha", "na", "ooh", "da",
        "gonna", "im", "dont", "aint", "wont", "yeah", "la", "oi", "nigga", "fuck",
          "hey", "year", "years", "last", "past", "feel","gotta","get","got","can")) %>%
  tm_map(removeNumbers)%>%
  tm_map(stripWhitespace)%>%
  tm_map(leadingWhitespace)%>%
  tm_map(stemDocument)

#save.corpus.to.files(corpus_c, filename = "corpus")

```

### Step 3. Transform corpuses to term document matrix.

Codes from the given [InteractiveWordCloud.Rmd](https://github.com/TZstatsADS/ADS_Teaching/blob/master/Tutorials/wk2-TextMining/doc/InteractiveWordCloud.Rmd)

Sava the tdm file as RData
```{r echo = FALSE}
### hiphop
tdm.h<-TermDocumentMatrix(corpus_h)
tdm.tidy.h=tidy(tdm.h)
tdm.overall.h=summarise(group_by(tdm.tidy.h, term), sum(count))

save(tdm.h, file="/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/output/tdm.h.RData")
### country
tdm.c<-TermDocumentMatrix(corpus_c)
tdm.tidy.c=tidy(tdm.c)
tdm.overall.c=summarise(group_by(tdm.tidy.c, term), sum(count))

save(tdm.c, file="/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/output/tdm.c.RData")
```

### Step 4. Compare bar charts of the top 10 frequent words in hiphop and country lyrics

Code from [STHDA](http://www.sthda.com/english/wiki/text-mining-and-word-cloud-fundamentals-in-r-5-simple-steps-you-should-know)
```{r echo = FALSE}
par(mfrow=c(1,2))
#hiphop
m.h <- as.matrix(tdm.h)
v.h<- sort(rowSums(m.h),decreasing=TRUE)
d.h <- data.frame(word = names(v.h),freq=v.h)

barplot(d.h[1:10,]$freq, las = 2, names.arg = d.h[1:10,]$word,
        col ="lightblue", main ="Most frequent words in hiphop lyrics",
        ylab = "Word frequencies")

#country
m.c <- as.matrix(tdm.c)
v.c <- sort(rowSums(m.c),decreasing=TRUE)
d.c <- data.frame(word = names(v.c),freq=v.c)

barplot(d.c[1:10,]$freq, las = 2, names.arg = d.c[1:10,]$word,
        col ="pink", main ="Most frequent words in country lyrics",
        ylab = "Word frequencies")
```


We can see that "love" and "time" are frequently used in both hiphop and country musics. However, by observing the words, the basic tones of two genres seems to be different.

### Step 5. Inspect wordclouds

Codes from the given [InteractiveWordCloud.Rmd](https://github.com/TZstatsADS/ADS_Teaching/blob/master/Tutorials/wk2-TextMining/doc/InteractiveWordCloud.Rmd)
```{r, fig.height=6, fig.width=6, echo = FALSE}
par(mfrow=c(1,2))
### hiphop
wordcloud(tdm.overall.h$term, tdm.overall.h$`sum(count)`,
          scale=c(5,0.5),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=F,
          colors=brewer.pal(8, "Dark2"))

### country
wordcloud(tdm.overall.c$term, tdm.overall.c$`sum(count)`,
          scale=c(5,0.5),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8, "Dark2"))
```

### Step.6 Sentiment Analysis 

Code from [Brian Ward](https://towardsdatascience.com/a-light-introduction-to-text-analysis-in-r-ea291a9865a8)

After observing the frequency chart and word cloud, we expect that the sentiment of Hophop is more negative than of Countrys. Let's do the sentiment analysis and have a look of the scores.

In this step we get the summaries and plots of sentimentGI scores, also top 5 and bottom 5 songs for both genre by the score.
```{r echo = FALSE}
### hiphop
sent.h <- analyzeSentiment(tdm.h, language = "english", removeStopwords = TRUE, stemming = TRUE)
# were going to just select the Harvard-IV dictionary results ..  
sent.h <- sent.h[,1:4]
#Organizing it as a dataframe
sent.h <- as.data.frame(sent.h)
sent.h <- cbind(sent.h,genre=hiphop$genre)

# Now lets take a look at what these sentiment values look like. 
summary(sent.h$SentimentGI)
```
The mean and median of the Hiphop sentimentGI score are both negative, which indicates that overall it's negative.

```{r echo = FALSE}
# See top and bottom songs based on the sentiment scores
final.h <- bind_cols(hiphop, sent.h)
# now lets get the top 5 
top.h <- final.h %>% group_by(song) %>%
  summarize(sent.h = mean(SentimentGI)) %>%
  arrange(desc(sent.h)) %>%
  head(n= 5)
# bottom 5
bottom.h <- final.h %>% group_by(song) %>%
  summarize(sent.h = mean(SentimentGI)) %>%
  arrange(sent.h) %>%
  head(n= 5)

rank.h <- cbind(top.h,bottom.h)
rank.h
save(rank.h, file="/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/output/hiphopSentRank.RData")

```
The first column are the songs with the five highest sentimentGI score.(Positive)
The third column are the songs with the five lowest sentimentGI score.(Negative)
It makes sense that those song names are matched with the sentiment.

```{r echo = FALSE}
# country-----------------------------------------------------------------------------------------------
sent.c <- analyzeSentiment(tdm.c, language = "english", removeStopwords = TRUE, stemming = TRUE)
sent.c <- sent.c[,1:4]
sent.c <- as.data.frame(sent.c)
sent.c <- as.data.frame(sent.c)
sent.c <- cbind(sent.c,genre=country$genre)
summary(sent.c$SentimentGI)
```
The mean and median of the country sentimentGI score are both negative, which indicates that overall it's positive.

```{r echo = FALSE}
final.c <- bind_cols(country, sent.c)
#  top 5 
top.c <- final.c %>% group_by(song) %>%
  summarize(sent.c = mean(SentimentGI)) %>%
  arrange(desc(sent.c)) %>%
  head(n= 5)

#bottom 5
bottom.c <- final.c %>% group_by(song) %>%
  summarize(sent.c = mean(SentimentGI)) %>%
  arrange(sent.c) %>%
  head(n= 5)

rank.c <- cbind(top.c,bottom.c)
rank.c
save(rank.c, file="/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/output/countrySentRank.RData")

```
Similar with the outcome of hiphop, this country song names match with the sentiment

Now visualize it to get more details.
```{r echo = FALSE}
par(mfrow=c(1,2))
ggplot(sent.h, aes(x = genre, y = SentimentGI, color = genre)) + 
  geom_boxplot() 
ggplot(sent.c, aes(x = genre, y = SentimentGI, color = genre)) + 
  geom_boxplot() 
```
The plot consistent with our former conclusion. Hiphop below 0 and country above 0. Moreover, both genres have more positive songs that negative songs.

### Step.7 Emotions Analysis

Code from [Brian Ward](https://towardsdatascience.com/a-light-introduction-to-text-analysis-in-r-ea291a9865a8)

In this step we compare the distributions of emotions of hiphop and country lyrics by generating the bar chart.
```{r echo = FALSE}
#hiphop
sent2.h <- get_nrc_sentiment(hiphop$lyrics)
sent3.h <- as.data.frame(colSums(sent2.h))
sent3.h <- rownames_to_column(sent3.h) 
colnames(sent3.h) <- c("emotion", "count")

#country
sent2.c <- get_nrc_sentiment(country$lyrics)
# Let's look at the corpus as a whole again:
sent3.c <- as.data.frame(colSums(sent2.c))
sent3.c <- rownames_to_column(sent3.c) 
colnames(sent3.c) <- c("emotion", "count")

# plots
par(mfrow=c(1,2))

ggplot(sent3.h, aes(x = reorder(emotion,-count), y = count, fill = emotion)) + 
  geom_bar(stat = "identity") + 
  theme_minimal() + 
  theme(legend.position="none", panel.grid.major = element_blank()) + 
  labs( x = "Emotion", y = "Total Count") + 
  ggtitle("Sentiment of hiphop lyrics") + 
  theme(plot.title = element_text(hjust=0.5))
ggplot(sent3.c, aes(x = reorder(emotion,-count), y = count, fill = emotion)) + 
  geom_bar(stat = "identity") + 
  theme_minimal() + 
  theme(legend.position="none", panel.grid.major = element_blank()) + 
  labs( x = "Emotion", y = "Total Count") + 
  ggtitle("Sentiment of country lyrics") + 
  theme(plot.title = element_text(hjust=0.5))
```


We can see that other than "positive" and "negative", the most frequently used emotion of hiphop is "fear" whereas for country is "joy". which is consistent with our guess again.

### Step.8 Topic Modeling 

code from [Tutorial(Week 2)](http://tzstatsads.github.io/tutorials/wk2_TextMining.html) and [tidytextmining](https://www.tidytextmining.com/topicmodeling.html#latent-dirichlet-allocation )

The goal is to make a heat map to see if Hiphop and Country lyrics share similar topics.

The dataset used in this step is new.RData. Use method and set k = 5 to get 5 topics from the hiphop and coutry lyrics.
First convert the corpus to document term matrix. Then use LDA to get the topics and the terms in each topic by beta value.
Then clustering the data frame and make the heat map.
```{r echo = FALSE}
#wk2 
corpus.list=NULL
for(i in 1:nrow(new)){
  sentences=syuzhet::get_sentences(new$lyrics[i])
  if(length(sentences)>0){
    
    corpus.list=rbind(corpus.list, 
                        cbind(new[i,-ncol(new)]
                              )
    )
  }
}
save(corpus.list,file="/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/output/corpus.list.RData")
```

# LDA

```{r echo = FALSE}
# set a seed so that the output of the model is predictable
dtm <-DocumentTermMatrix(corpus_b)
save(dtm,file="/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/output/dtm.RData")
k <- 5
ldaOut <- LDA(dtm, k, control = list(seed = 1234))
ldaOut.topics <- as.matrix(topics(ldaOut))
# get topic terms
terms.beta=ldaOut@beta
terms.beta=scale(terms.beta)

topics.terms=NULL
for(i in 1:k){
  topics.terms=rbind(topics.terms, ldaOut@terms[order(terms.beta[i,], decreasing = TRUE)[1:8]])
}
ldatopics <- tidy(ldaOut, matrix = "beta")
topicProbabilities <- as.data.frame(ldaOut@gamma)

topics.terms
save(topics.terms, file="/Users/meow/Documents/GitHub/Spring2020-Project1-meow530/output/LDATopicTerm.RData")

```

```{r echo = FALSE}
# get ldaOut.terms
ldaOut.terms <- ldatopics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

# visualization
ldaOut.terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  scale_x_reordered()


```

```{r echo = FALSE}
# topics hash
topics.hash=c("Topic 1", "Topic 2", "Topic 3","Topic 4","Topic 5")
corpus.list$ldatopic=as.vector(ldaOut.topics)
corpus.list$ldahash=topics.hash[ldaOut.topics]
colnames(topicProbabilities)=topics.hash
corpus.list.df=cbind(corpus.list, topicProbabilities)
head(corpus.list.df)


#clustering
par(mar=c(1,1,1,1))
topic.summary=tbl_df(corpus.list.df)%>%
              select(genre,"Topic 1":"Topic 5")%>%
              group_by(genre)%>%
              summarise_each(funs(mean))
topic.summary=as.data.frame(topic.summary)
rownames(topic.summary)=topic.summary[,1]
topic.plot=2:6

# heatmap
heatmap.2(as.matrix(topic.summary[,topic.plot]), 
          scale = "column", key=F, 
          col = bluered(100),
          cexRow = 0.9, cexCol = 0.9, margins = c(8, 8),
          trace = "none", density.info = "none")

```


Based on the heat map, it is clear that Hiphop and country lyrics share different topics.

### Conclusion

By observing the word frequency, word cloud, sentimentGI score, emotions distribution and the topics analysis, we can conclude that Hip-hop and Country music lyrics are significantly different.

Hip-hop lyrics tend to be more negative. The words associated with "fear" are used frequently. Whereas Country lyrics are more warm and positive. The words associated with "joy" are used frequently.

Eventhough two genres' lyrics give different feeling, "Love" is the most popular theme for both.

This conclusion also consistent with our guess by the definitions and cultures.

